---
title: "Rocky Shore Tanaids Compostion"
author: "Chih-Lin Wei"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, dev='jpeg', dpi = 600)
```

```{r}
# library(devtools)
# install_github('AnneChao/iNEXT.3D')
## import packages
library(iNEXT.3D)
library(readxl)
library(reshape2)
library(doBy)
library(dplyr)
library(plyr)
library(stringr)
library(ggplot2)
library(vegan)
library(ggdendro)
library(patchwork)
```

# ggplot theme setting

```{r}
large <- theme(legend.title = element_text(size=15),
        legend.text = element_text(size=15),
        axis.title = element_text(size=15),
        axis.text = element_text(size=15),
        strip.text = element_text(size=15))

rotate <- theme(axis.text.x = element_text(angle = 90, hjust=1))

no_strip <- theme(strip.background = element_rect(colour=NA, fill=NA),
                  strip.text = element_text(colour=NA))
```

# Preparing tanaid data

```{r}
ta0 <- read_excel("../Data/Tanaidacea community.xlsx", sheet = 3)
ta <- ta0[, 1:2]
# Create factor "Microhabitat"
ta$Microhabitat <- str_replace(ta0$Microhabitat, " \\s*\\([^\\)]+\\)", "")
# Create factor "Replicate"
ta$Replicate <- str_extract(ta0$Microhabitat, "(?<=\\()\\d+(?=\\))")
ta <- cbind(ta, ta0[,-1:-3])
# Remove zero rows
ta <- ta[rowSums(ta0[,-1:-3])!=0, ]
ta$Site <- factor(ta$Site, levels=c("Shitiping", "Jihuei", "Jialulan"), labels = c("STP", "JH", "JLL"))
ta$Season <- factor(ta$Season, levels = c("SP", "SU"), labels = c("AP", "AU"))
# Only keep data for analysis
b <- ta[, -1:-4]
rownames(b) <- with(ta, paste(Site, Season, Microhabitat, Replicate, sep="_"))
```

# Prepare CWB data

```{r}
library(rjson)
library(dplyr)

cwb <-  fromJSON(file="../Data/C-B0050-001.json")

# Meta data 
meta <- lapply(cwb$cwbdata$Resources$Resource$Data$SeaSurfaceObs$Location, FUN=function(x)x[[1]])

# Monthly temperature
dat <- lapply(cwb$cwbdata$Resources$Resource$Data$SeaSurfaceObs$Location, FUN=function(x)x[[2]]$Monthly)

MonthlyTemperatureFun <- function(i){
  cbind(StationNameEN = lapply(meta, FUN=function(x)x$StationNameEN)[i] %>% as.character %>% as.factor,
        cbind(
          StationLatitude=lapply(meta, FUN=function(x)x$StationLatitude)[i] %>% as.numeric,
          StationLongitude=lapply(meta, FUN=function(x)x$StationLongitude)[i] %>% as.numeric,
          DataMonth=lapply(dat[[i]], FUN=function(x)x$DataMonth) %>% unlist %>% as.numeric,
          Maximum=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$Maximum) %>% unlist %>% as.numeric,
          MaximumYear=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$MaximumYear) %>% unlist %>% as.numeric,
          Mean=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$Mean) %>% unlist %>% as.numeric,
          Minimum=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$Minimum) %>% unlist %>% as.numeric,
          MinimumYear=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$MinimumYear) %>% unlist %>% as.numeric,
          MinimumAnomaly=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$MinimumAnomaly) %>% unlist %>% as.numeric,
          MaximumAnomaly=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$MaximumAnomaly) %>% unlist %>% as.numeric,
          MeanAnomaly=lapply(dat[[i]], FUN=function(x)x$SeaTemperature$MeanAnomaly) %>% unlist %>% as.numeric
          ) %>% as.data.frame
  )
}

# Hualien Buoy
hb <- MonthlyTemperatureFun(18) %>% subset((DataMonth=="4"|DataMonth=="8") & MinimumYear == "2012" & MaximumYear == "2012")
# Chenggong
cg <- MonthlyTemperatureFun(8) %>% subset((DataMonth=="4"|DataMonth=="8") & MinimumYear == "2012" & MaximumYear == "2012")
# Taitung Buoy
tb <- MonthlyTemperatureFun(34) %>% subset((DataMonth=="4"|DataMonth=="8") & MinimumYear == "2012" & MaximumYear == "2012")

tmp <- rbind(hb, cg, tb)
```


# Aggregate by microhabitat

```{r}
ta2 <- aggregate(b, by = list(ta$Site, ta$Season), FUN=sum)
names(ta2)[1:2] <- c("Site", "Season")
b2 <- ta2[, -1:-2]
rownames(b2) <- with(ta2, paste(Site, Season, sep="_"))
```

# Estimate Hill Numbers

* Bootstrap confidence interval (1000 iterations)
```{r, eval=FALSE}
q0 <- iNEXT3D(t(b2), diversity = "TD", q = 0, nboot=1000)
q1 <- iNEXT3D(t(b2), diversity = "TD", q = 1, nboot=1000)
q2 <- iNEXT3D(t(b2), diversity = "TD", q = 2, nboot=1000)
#save(list=c("q0", "q1", "q2"), file="HillNumbersTD.rda")
```

```{r, fig.width=12, fig.height=4}
load("../Data/HillNumbersTD.rda")

h <- rbind(q0$iNextEst$size_based,
           q1$iNextEst$size_based,
           q2$iNextEst$size_based)
h <- cbind(h, ta2[match(h$Assemblage, rownames(b2)), 1:2])
h$Season <- factor(h$Season, labels=c("SP", "SU"))
```

Fig. X. Size-based diversity accumulation curves based on spe richness (left), effective number of typical species (middle) and effective number of dominant species (right). The blue lines indicate the interpolated (rarefied) and red lines indicate extrapolated parts of the accumulation curves based on 1000 permutations. Dotted symbols indicate the observed diversity values.

```{r, fig.width=12, fig.height=4}
# Minimum sample coverage for each order q
min(ldply(lapply(splitBy(~Order.q+Assemblage, subset(h, Order.q==0)), FUN=function(x)x[dim(x)[1],]))$SC)
min(ldply(lapply(splitBy(~Order.q+Assemblage, subset(h, Order.q==1)), FUN=function(x)x[dim(x)[1],]))$SC)
min(ldply(lapply(splitBy(~Order.q+Assemblage, subset(h, Order.q==2)), FUN=function(x)x[dim(x)[1],]))$SC)
# SC = 0.99
```

```{r}
h1 <- subset(h, Order.q ==0 & SC <= 0.9957578)

p1 <- ggplot()+
  geom_ribbon(data=h1,
              aes(x=m, ymin=qD.LCL, ymax=qD.UCL, group=Assemblage, fill=Site), alpha=0.2)+
  geom_line(data= subset(h1, Method=="Rarefaction"), 
            aes(x=m, y=qD, group=Assemblage, colour=Site), size=0.8)+
  geom_line(data= subset(h1, Method=="Extrapolation"), 
            aes(x=m, y=qD, group=Assemblage, colour=Site), linetype=2, size=0.8)+
  geom_point(data= subset(h1, Method=="Observed"), 
             aes(x=m, y=qD, group=Assemblage))+
  scale_fill_viridis_d()+
  scale_color_viridis_d()+
  facet_wrap(~Season, scale="free")+
  labs(x = "Numbers of Individuals", y = expression(Species~Richness~(""^0*italic(D))),
       colour="Site")+
  theme_bw()%+replace% large %+replace% theme(axis.text.x = element_blank(), axis.title.x = element_blank())
```

```{r}
h2 <- subset(h, Order.q ==1 & SC <= 0.9957578)

p2 <- ggplot()+
  geom_ribbon(data=h2,
              aes(x=m, ymin=qD.LCL, ymax=qD.UCL, group=Assemblage, fill=Site), alpha=0.2)+
  geom_line(data= subset(h2, Method=="Rarefaction"), 
            aes(x=m, y=qD, group=Assemblage, colour=Site), size=0.8)+
  geom_line(data= subset(h2, Method=="Extrapolation"), 
            aes(x=m, y=qD, group=Assemblage, colour=Site), linetype=2, size=0.8)+
  geom_point(data= subset(h2, Method=="Observed"), 
             aes(x=m, y=qD, group=Assemblage))+
  scale_fill_viridis_d()+
  scale_color_viridis_d()+
  facet_wrap(~Season, scale="free")+
  labs(x = "Numbers of Individuals", y = expression(Species~Richness~(""^1*italic(D))),
       colour="Site")+
  theme_bw()%+replace% large %+replace% theme(legend.position = "none")
```

```{r, fig.width=10, fig.height=6}
p1/p2
```

```{r}
p3 <- ggplot()+
  geom_ribbon(data=h1,
              aes(x=SC, ymin=qD.LCL, ymax=qD.UCL, group=Assemblage, fill=Site), alpha=0.2)+
  geom_line(data= subset(h1, Method=="Rarefaction"), 
            aes(x=SC, y=qD, group=Assemblage, colour=Site), size=0.8)+
  geom_line(data= subset(h1, Method=="Extrapolation"), 
            aes(x=SC, y=qD, group=Assemblage, colour=Site), linetype=2, size=0.8)+
  geom_point(data= subset(h1, Method=="Observed"), 
             aes(x=SC, y=qD, group=Assemblage))+
  scale_fill_viridis_d()+
  scale_color_viridis_d()+
  facet_wrap(~Season, scale="free")+
  labs(x = "Sample Completeness", y = expression(Species~Richness~(""^0*italic(D))),
       colour="Site")+
  theme_bw()%+replace% large %+replace% theme(axis.text.x = element_blank(), axis.title.x = element_blank())
```

```{r}
p4 <- ggplot()+
  geom_ribbon(data=h2,
              aes(x=SC, ymin=qD.LCL, ymax=qD.UCL, group=Assemblage, fill=Site), alpha=0.2)+
  geom_line(data= subset(h2, Method=="Rarefaction"), 
            aes(x=SC, y=qD, group=Assemblage, colour=Site), size=0.8)+
  geom_line(data= subset(h2, Method=="Extrapolation"), 
            aes(x=SC, y=qD, group=Assemblage, colour=Site), linetype=2, size=0.8)+
  geom_point(data= subset(h2, Method=="Observed"), 
             aes(x=SC, y=qD, group=Assemblage))+
  scale_fill_viridis_d()+
  scale_color_viridis_d()+
  facet_wrap(~Season, scale="free")+
  labs(x = "Sample Completeness", y = expression(Species~Richness~(""^1*italic(D))),
       colour="Site")+
  theme_bw()%+replace% large %+replace% theme(legend.position = "none")
```

```{r, fig.width=10, fig.height=6}
p3/p4
```

```{r}
fr <- strsplit(q0$DataInfo$Assemblage, split="_") %>% ldply
names(fr) <- c("Site", "Season")
fr$Season <- factor(fr$Season, labels=c("SP", "SU"))
h1_out <- lapply(splitBy(~Assemblage, h1), FUN=function(x)tail(x, n=1)) %>% ldply
h2_out <- lapply(splitBy(~Assemblage, h2), FUN=function(x)tail(x, n=1)) %>% ldply
```

```{r}
t0 <- cbind(cbind(fr, S.obs = q0$DataInfo$S.obs), tmp[c(1, 3, 5, 2, 4, 6),]) 
t0$Site <- factor(t0$Site, levels=c("STP", "JH", "JLL"))
t1 <- cbind(h1_out, tmp[c(1, 3, 5, 2, 4, 6),])
t2 <- cbind(h2_out, tmp[c(1, 3, 5, 2, 4, 6),])
h2 <- readRDS("../Data/H2.rds")
h2$Site <- factor(h2$Site, levels=c("STP", "JH", "JLL"))
```

```{r}
pv <- round(summary(lm(S.obs~Mean, data=t0))$coefficients[2, 4], 3)
r2 <- round(summary(lm(S.obs~Mean, data=t0))$adj.r.squared, 2)
f <- round(summary(lm(S.obs~Mean, data=t0))$fstatistic[1], 2)
label = paste0("italic(F)['1,4'] ==", f, "*','~P==", pv, "*','~italic(R)^2 ==", r2)

p7 <- ggplot(data=t0, aes(x=Mean, y=S.obs, shape=Season, colour=Site))+
  geom_point(size=2, stroke=1.5)+
  stat_smooth(formula=y~x, method = "glm", aes(group=1), alpha=0.2, colour="gray", linetype=2)+
  annotate(geom = "text", x = 24, y = 12.5, hjust = 0, vjust = 1, label = label, parse = TRUE) +
  scale_color_viridis_d()+
  scale_shape_manual(values=c(1,19))+
  labs(x = expression(Temperature~(degree~C)), y = "Numbers of Species", title="a")+
  theme_bw() %+replace% large %+replace% theme(axis.text.x = element_blank(), axis.title.x = element_blank(), legend.position = "none")
```

```{r}
pv <- round(summary(lm(qD~Mean, data=t1))$coefficients[2, 4], 3)
r2 <- round(summary(lm(qD~Mean, data=t1))$adj.r.squared, 2)
f <- round(summary(lm(qD~Mean, data=t1))$fstatistic[1], 2)
label = paste0("italic(F)['1,4'] ==", f, "*','~P==", pv, "*','~italic(R)^2 ==", r2)

p8 <- ggplot(data=t1, aes(x=Mean, y=qD, ymin=qD.LCL, ymax=qD.UCL, shape=Season, colour=Site))+
  geom_point(size=2, stroke=1.5)+
  geom_errorbar()+
  stat_smooth(formula=y~x, method = "glm", aes(group=1), alpha=0.2, colour="gray", linetype=2)+
  annotate(geom = "text", x = 24.5, y = 22, hjust = 0, vjust = 1, label = label, parse = TRUE) +
  scale_color_viridis_d()+
  scale_shape_manual(values=c(1,19))+
  labs(x = expression(Temperature~(degree~C)), y = expression(Species~Richness~(""^0*italic(D))), title="b")+
  theme_bw() %+replace% large %+replace% theme(axis.text.x = element_blank(), axis.title.x = element_blank())
```

```{r}
pv <- round(summary(lm(qD~Mean, data=t2))$coefficients[2, 4], 3)
r2 <- round(summary(lm(qD~Mean, data=t2))$adj.r.squared, 2)
f <- round(summary(lm(qD~Mean, data=t2))$fstatistic[1], 2)
label = paste0("italic(F)['1,4'] ==", f, "*','~P==", pv, "*','~italic(R)^2 ==", r2)

p9 <- ggplot(data=t2, aes(x=Mean, y=qD, ymin=qD.LCL, ymax=qD.UCL, shape=Season, colour=Site))+
  geom_point(size=2, stroke=1.5)+
  geom_errorbar()+
  stat_smooth(formula=y~x, method = "glm", aes(group=1), alpha=0.2, colour="gray", linetype=2)+
  annotate(geom = "text", x = 24, y = 6, hjust = 0, vjust = 1, label = label, parse = TRUE) +
  scale_color_viridis_d()+
  scale_shape_manual(values=c(1,19))+
  labs(x = expression(Temperature~(degree~C)), y = expression(Shannon~Diversity~(""^1*italic(D))), title="c")+
  theme_bw()%+replace% large %+replace% theme(legend.position = "none")
```

```{r}
pv <- round(summary(lm(H2~Mean, data=h2))$coefficients[2, 4], 3)
r2 <- round(summary(lm(H2~Mean, data=h2))$adj.r.squared, 2)
f <- round(summary(lm(H2~Mean, data=h2))$fstatistic[1], 2)
label = paste0("italic(F)['1,4'] ==", f, "*','~P==", pv, "*','~italic(R)^2 ==", r2)

p10<- ggplot(data=h2, aes(x=Mean, y=H2, ymin=X1, ymax=X2, shape=Season, colour=Site))+
  geom_point(size=2, stroke=1.5)+
  geom_errorbar()+
  stat_smooth(formula=y~x, method = "glm", aes(group=1), alpha=0.2, colour="gray")+
  annotate(geom = "text", x = 24.5, y = 0.95, hjust = 0, vjust = 1, label = label, parse = TRUE) +
  scale_color_viridis_d()+
  scale_shape_manual(values=c(1,19))+
  labs(x = expression(Temperature~(degree~C)), y = "H2' index", title="d")+
  theme_bw()%+replace% large %+replace% theme(legend.position = "none")
```

```{r, fig.width=8, fig.height=8}
(p7+p8)/(p9+p10)
```

```{r}
library(knitr)
kable(t0)
kable(t1)
kable(t2)
```

